%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{hyperref}


% Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Saket Harsh} % Your name

\address{2nd Year Undergraduate }
\address{Hall 3, IIT Kanpur, U.P 208016}
% Your a
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(+91)~7755~042~551  \href{mailto:sharsh@iitk.ac.in}{\textbf{sharsh@iitk.ac.in}}} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{ \hspace{.5cm} Education}

{\bf Indian Institute of Technology Kanpur} \hfill {\em July 2015 - Present} 
\\ 4yr B.S. in Mathematics \& Sc. Computing \hfill { Overall GPA: 7.8/10}
\\ Department Of Mathematics\\ \\
{\bf Delhi Public School, Ranchi} \hfill {\em June 2013 - May 2015} 
\\ AISSCE(Class 12th Board) \hfill { Precentage 95.8 \%}
\\ Computer Science as 5th Subject\\ \\
{\bf Oxford Public School, Ranchi} \hfill {\em May 2010 - May 2013} 
\\ AISSE(Class 10th Board) CBSE \hfill { Overall GPA:10/10}
 
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Academic Achievements} \itemsep -2pt
\item \textbullet All India Rank \textbf{35} in \textbf{SCRA(Special Class Railway Apprentice 2015)}  organized by \textbf{UPSC}
\item  \textbullet All India Rank \textbf{768} in JEE MAIN 2015 organized by \textbf{CBSE}
\item  \textbullet State wise top \textbf{1\% } in \textbf{NSEP}(National Standard Examination in Physics) organized by \textbf{IAPT} 
\item  \textbullet State Rank \textbf{3} in I.T Talent Search Examination 2008 , Jharkhand State 
\end{rSection}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
 Languages &  C/C++, MATLAB, Python, Shell Scripting, HTML \\
Software \& Tools &  \LaTeX,Git, Solidworks, GNUPlot, Vim, MySQL \\
Operating System & Ubuntu, Arch Linux, Fedora, Mac OS, MS Windows
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{ Projects}

\begin{rSubsection}{Machine Learning}{May 2016 - July 2016}{Programming Club, IIT Kanpur}{}
\item Studied about different Machine learning techniques and implemented a Neural Network based Machine Learning Algorithm to predict the closing Stocks of various Multi-National Companies. 
\item Collected dataset of various MNC's of about an year to train a 4*70*50*1 neural network for the desired output. 
\end{rSubsection}


%------------------------------------------------

\begin{rSubsection}{RmSearch}{December 2016 }{Self Undertaken Project}{}
\item Wrote a script in \textbf{Python} and \textbf{Shell} to search for any .mp3 file in the Computer and Play it using command line VLC.
\item Script is able to recognize mp3 songs even by incomplete names(up to an extent).
\item  Visit \href{https://github.com/saketharsh/RmSearch}{github.com/saketharsh/RmSearch} for more details.
\end{rSubsection}

\begin{rSubsection}{Mechanical Elevator}{3rd Semester 2016-17 }{Prof. Rajiv Shekhar}{}
\item Learnt basic techniques of working with metals(Brazing,Welding,Casting).
\item Implemented the techniques to build a Mechanical Elevator that can lift Objects which are elliptic in nature to large heights by mechanical forces only.
\end{rSubsection}
\end{rSection}


\begin{rSection}{Relevant Courses}
\itab{\textbf{1st and 2nd Semester}} \tab{}  \tab{\textbf{3rd and 4th Semester}}
\\ \itab{Introduction to Computing} \tab{} \tab{Computational Methods in Engineering}
\\ \itab{Introduction to Mechanics} \tab{} \tab{Abstract Algebra} 
\\ \itab{Linear Algebra and Ordinary Differential Equations} \tab{}  \tab{Probability and Statistics*} 
\\ \itab{Introduction to Economics} \tab{} \tab{Real Analysis}
\\ \itab{Multivariable Calculus} \tab{} \tab{Mathematical Logic*} 
% \\ \itab{Process Control (ongoing)} \tab{} \tab{Electrodynamics}
\tab{} \tab{} \tab{} \hfill{* marked course are undergoing}

\end{rSection}


\end{rSection}


\begin{rSection}{\hspace{.7cm} POSITION OF RESPONSIBILITY}

\begin{rSubsection}{Programming Club , IIT Kanpur }{August 2016 - Present}{Secretary}{IIT Kanpur}
\item Currently working with a team of 30 Computer Enthusiasts to conduct, organize, and promote all kinds of Programming Related activities inside the Campus.
\item Successfully organized Linux Install Fest to promote Open Source Contribution in the Campus. 
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Counselling Service, IIT Kanpur}{April 2016 - Present}{Student Guide}{IIT Kanpur}
\item Selected for the post of Student Guide , to guide six incoming students for smooth transition into their lives away from home and to help them in their ups and downs  at IIT Kanpur.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{\hspace{.5cm} Interests and Extra- Curricular Activities} \itemsep -3pt
\item \textbf{Machine Learning}, \textbf{Competitive Programming} and \textbf{Open Source Contribution} are the interests that I pursue in general. 
\item Completed a year long training in \textbf{Football as a Physical Activity Course} 
\item Participated in \textbf{Electromania, Takneek 2015}(Inter Hall Technical Competition) to develop a "Bucket Game" using LED's, IC, and breadboards.
\item Actively participated in Quizzes, Debates and Calligraphy in school.

 % \item Member, Athletics Team, IIT Kanpur. Attended Summer Sport Camp as a long jumper.
%\item Trained and disciplined in National Cadet Corps (NCC), IIT Kanpur for a year.
 %\item  Participated in Vijyoshi Camp 2012 organized at Indian Institute of Science, Bangalore.
 %\item Won 2nd position in Kho-Kho in Intramurals conducted by Physical Education Section, IIT Kanpur.
 %\item Pursued French as second language during secondary school from Grade 6 to Grade 10. Also participated in French Song Competition and French G.K. Quiz in Class 10th. %

\end{rSection}

\end{document}
