%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Saket}{Harsh}{ \urlstyle{same}\url{http://saketharsh.wordpress.com} \\
{Address- Room No 257 Hall 3 IIT Kanpur PIN -208016} \\
\href{mailto:sharsh@iitk.ac.in.edu}{sharsh@iitk.ac.in} | (+91)7755 042 551
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{IIT Kanpur}
\descript{4 Yr B.S in Mathematics \& Sc. Computing}
\location{2015-2019(Expected) \\ Cumulative. GPA: 7.8/10}
\sectionsep

\subsection{AISSCE(CBSE Class 12th)}
\descript{Delhi Public School}
\location{Sail Township, Ranchi, Jharkhand}
\location{ Percentage- 95.8\% 
}
\sectionsep

\subsection{AISSE(CBSE Class 10th)}
\descript{Oxford Public School,Ranchi}
\sectionsep{ CGPA- 10/10}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
C \textbullet{}   C++ \textbullet{} Python \textbullet{} Matlab \\
\textbullet{} Shell Scripting  \textbullet{} HTML \\ 
\subsection{Operating Systems}
Linux(Ubuntu) \textbullet{} Fedora \textbullet{} Arch Linux \\
\textbullet{} Windows  
\subsection{Utilities}
Vim \textbullet{} Git \textbullet{} \LaTeX
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Ongoing}
Probability and Statistics \\
Mathematical Logic \\
Ordinary Differential Equations \\


\sectionsep

\subsection{Completed}
Introduction to Computing \\
Abstract Algebra\\
Real Analysis \\
Numerical Methods Of Computation \\
Linear Algebra \\
Introduction to Calculus
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Links
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/saketharsh}{\custombold{saketharsh}} \\
LinkedIn://  \href{https://www.linkedin.com/in/saket-harsh-iitk}{\custombold{saket-harsh-iitk}} \\
Quora://  \href{https://www.quora.com/Saket-Harsh}{\custombold{Saket-Harsh}}
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Project}

\runsubsection{Machine Learning}
\descript{| Programming Club, IIT Kanpur }
\location{May 2016-July 2016 | IIT Kanpur}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Studied about different Machine learning techniques and implemented a Neural Network based Machine Learning Algorithm to predict the closing Stocks of various MNC's. 
\item Collected dataset of various MNC's of about an year to train a 4*70*50*1 neural network for the Desired output. 
\end{tightemize}
\sectionsep

\runsubsection{RmSearch}
\descript{| Self Undertaken Project }
\location{Dec 2016 }
\begin{tightemize}
\item Wrote a script in Pyhton and Shell to search for any .mp3 file in the Computer and Play it using command line VLC.
\item Script able to recognize Mp3 songs even by incomplete names(upto an extent).
\item Github:// \href{https://github.com/saketharsh/RmSearch}{\custombold{saketharsh/RmSearch}} \\
\end{tightemize}
\sectionsep

\runsubsection{Mechanical Elevator}
\descript{| Technical Arts Course Project, }
\location{3rd Semester, Prof. Rajiv Shekhar }
\begin{tightemize}
\item Learnt basic techniques of working with metals(Brazing,Welding,Casting).
\item Implemented the techniques to build a Mechanical Elevator that can lift Objects which are elleptic in nature to large heights by mechanical forces only. 
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Scholastic Achievement} 
\begin{tabular}{rll}
2015	     & AIR 35  & SCRA(Special Class Railway Apprentice) organised by UPSC\\
2015	     & AIR 768  & JEE Main 2015 organised by CBSE \\
2015	     & Top 1\% student  & NSEP(National Standard Examination in Physics)\\
2013	     & State Rank 3 & I.T Talent Search Examination, Jharkhand State\\
\end{tabular}
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Position of Responsibility}
\runsubsection{Programming Club IITK}
\descript{| Secretary}
\location{Jun 2016 – Present | Kanpur}
Currently working with a passionate and hardworking team of Computer Enthusiasts within the campus to organise Programming related activities, and involved in differnt programming events taking place within the Campus.
\sectionsep

\runsubsection{Counselling Service, IIT Kanpur}
\descript{| Student Guide}
\location{June 2016}
Selected for the post of Student Guide , to guide six incoming students for smooth transition into their lives away from home and to help them int their lives at IIT Kanpur.
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Interests} 
Competitive Programming, Open Source Contribution, Machine Learning and Linux are the words that can describe my interests in all.



\sectionsep

\end{minipage} 
\end{document}